Incremental Forward Reasoning for White-Box~Proof~Search

### 2025-02-18 paper.tex
Minor edit in related work

The Prolog-based first-order theorem prover SATCHMO (TODO ref) and its many descendants also use mixed-mode reasoning.
SATCHMO's search procedure can be viewed as a special case of our technique: a given set of implications are used as forward rules and a single case-splitting rule splits any goal with hypothesis $h : B₁ ∨ \dots ∨ Bₘ$ into $m$ goals with hypotheses $h₁ : B₁, \dots, hₘ : Bₘ$.
A SATCHMO-style prover may benefit from our incremental approach if the set of implications is large, though in a setting where unification is cheap it is not clear whether avoiding repeated unifications outweighs the cost of maintaining the forward state.
SATCHMO also employs an optimisation that \enquote*{focuses} forward reasoning on the hypothesis established by the last case split, which provides a form of incrementality.

>>>>

The Prolog-based first-order theorem prover SATCHMO (TODO ref) and its many descendants also use mixed-mode reasoning.
SATCHMO's search procedure can be viewed as a special case of our technique: a given set of implications are used as forward rules and a single non-forward rule performs case analysis on disjunctive hypotheses.
A SATCHMO-style prover may benefit from our incremental approach if the set of implications is large, though in a setting where unification is cheap it is not clear whether avoiding repeated unifications outweighs the cost of maintaining the forward state.
SATCHMO also employs an optimisation that \enquote*{focuses} forward reasoning on the hypothesis established by the last case split, which provides a form of incrementality.
